Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm

### 2023-06-24 paper/main.tex
add magic
修改了方法部分的hat和main.png

@@

The overall MAC modeling process based on an RBS is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
In the first place, the actual switching circuit typology of the RBS is converted to a directed graph model, in which the connected relationships between batteries and switches are described by nodes and the performance parameters of the batteries are retained.
Subsequently, the allowable current of the RBS is regarded as an objective function to be obtained based on the previous connected relationships and parameters.
Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
In the end, an optimized switching circuit strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
% 问题出在 要用最简短、读者能接受的话描述清楚方法
% 重写上面一段，注意描述方法时的逻辑性

% main 主图只保留文字

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../attachments/main.png}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \\ 
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    % caption 简写
    \caption{ (a)Diagram of this method, which contains four main steps.
        Step 1: The RBS structure is converted to a topologic model.
        Step 2: Constraints and objective function are obtained based on the previous topologic model.
        Step 3: The shortest path of each battery in the RBS is obtained by Dijkstra algorithm.
        Step 4: The MAC is achieved by greedily selecting the shortest paths to open/close switches.
        (b) The equivalent circuit of a battery in this method, with $u_{b,i}$ and $r_{b,i}$ representing the voltage and internal resistance of the battery $i$ respectively.
        The capacitor in Thevenin model is ignored.
    }
\end{figure}

>>>>

% magic
% 你将扮演一位英文学术写作经验丰富的大学老师，指导一位非英文母语的学生完成并改进他的论文。 你的目标是帮助他写出一篇流畅、清晰、易读、符合规范的英文学术论文。 他会向你用中文说明自己想表达的内容，有时还会给你一些不完整的英文句子让你补充完整。你不应该逐字翻译他的内容，你需要和他经过多次的沟通，以确定最好的表达。 注意，你们交流的内容可能包含latex语法，你需要理解并使用；当你形成完整的句子或段落时，你要将这些句子或段落放在```和```之间，即 ```some sentence ```，其中每写完一句话都要换行。

@@

The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig. \ref{fig:main}.
Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in series.
Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../attachments/main.png}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \\ 
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    % caption 简写
    \caption{ 
        (a)Diagram of this method, which contains four main steps.
        (b) The equivalent circuit of a battery in this method.
    }
\end{figure}
